Get population and temperature data, version 2

### 2021-12-09 getdata2.Rmd
changes ...

The only (so far) difference compared to the article "getdata.Rmd" is that time 
here is measured in *days* instead of in a fraction of a year.

@@

```{r neo, fig.cap = "Neonatal mortality by year, all regions."}
neo <- births
##
##neo$birthdate <- toTime(neo$foddat)
neo <- age.window(neo, c(0, 28 / 365))
##neo$exit <- 365 * neo$exit
surv <- as.matrix(neo[, c("enter", "exit", "event", "birthdate")])
pall <- perstat(surv, period = 1900:1951)$intensity
plot(1900:1950, pall, type = "b", ylim = c(0, 0.5), col = "blue", xlab = "Year",
     ylab = "Mortality")
abline(h = 0)
abline(h = 0.3, lty = 3)
```

>>>>

The only (so far) difference compared to the article "getdata.Rmd" is that time 
here is measured in *days* instead of in a fraction of a year. *However*, "at the end", time is transformed back to units in years. The main reason is that the function `make.communal`
assumes time measured in years, it is probably the variable `birthdate` that is the culprit.
I will look into that in due course.

@@

```{r neo, fig.cap = "Neonatal mortality by year, all regions."}
neo <- births
par(las = 1)
##
##neo$birthdate <- toTime(neo$foddat)
neo <- age.window(neo, c(0, 28 / 365))
##neo$exit <- 365 * neo$exit
surv <- as.matrix(neo[, c("enter", "exit", "event", "birthdate")])
pall <- perstat(surv, period = 1900:1951)$intensity
plot(1900:1950, pall, type = "b", ylim = c(0, 0.7), col = "blue", xlab = "Year",
     ylab = "Mortality")
abline(h = 0)
abline(h = c(0.1, 0.3, 0.5) , lty = 3)
```
